K Nearest Neighbour Search Using Space-filling Curves

### 2013-12-07 paper/paper.tex
fixed the labeling of gray code inverse

\begin{algorithm}
  \caption{The algorithm for calculating the Gray Code Inverse of $g \in \mathbb{N}$, calculates the $i \in \mathbb{N}$ such that $gc\left( i \right) = g $ }
  \label{gray-code-inverse}
  \begin{algorithmic}[1]
    \Require $g \in \mathbb{N}$ 
    \State $ m \leftarrow \text{ number of bits to represent } g$ 
    \State $ \left( i, j \right) \leftarrow \left( g, 1 \right) $ 
    \While{$ j < m $ }
    \State $ i \leftarrow i \oplus \left( g \gg j \right)$ 
    \State $ j \leftarrow j + 1$ 
    \EndWhile \\
    \Return $i$ % \in \mathbb{N} \text{ such that } gc \left( i \right) = g $
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
  \caption{The algorithm for calculating the Gray Code Inverse $(gc^{-1}(g))$ of $g \in \mathbb{N}$, calculates the $i \in \mathbb{N}$ such that $gc\left( i \right) = g $ }
  \label{gray-code-inverse}
  \begin{algorithmic}[1]
    \Require $g \in \mathbb{N}$ 
    \State $ m \leftarrow \text{ number of bits to represent } g$ 
    \State $ \left( i, j \right) \leftarrow \left( g, 1 \right) $ 
    \While{$ j < m $ }
    \State $ i \leftarrow i \oplus \left( g \gg j \right)$ 
    \State $ j \leftarrow j + 1$ 
    \EndWhile \\
    \Return $i$ % \in \mathbb{N} \text{ such that } gc \left( i \right) = g $
  \end{algorithmic}
\end{algorithm}
